EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
rm clearpage
omit env. mock

% Mocking
\TODO{Add some stats on mocking}

@@

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
%\def\IEEEbibitemsep{6pt}
\clearpage
\bibliographystyle{IEEEtranS}
\bibliography{papers}
\balance

>>>>

% Mocking
As mentioned in the previous section, \EVOSUITE now uses private
API access and functional mocking%  in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
. Further
investigation is needed to assess the impact of these mocking features
on test generation effectiveness for the benchmarks in the competition.

@@

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
%\def\IEEEbibitemsep{6pt}
%\clearpage
\bibliographystyle{IEEEtranS}
\bibliography{papers}
\balance
